Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-16 text/paper2/ms.tex
some notes to self

\section{Scalings}

@@

a phase-space distance, $D_{ps}$, as the sum of the normalized, relative position, $\frac{\bs{r}-\bs{r}_p}{\rtide}$, and velocity, $\frac{\bs{v}-\bs{v}_p}{v_{\rm esc}}$, for a stream star. We minimized the generalized variance of the 6D distribution over each normalized coordinate evaluated at the time that each star has minimum $D_ps$. This simple idea proved quite powerful for constraining properties of the LM10 potential used simulated observations of their N-body simulation. However, this method does not properly incorporate observational uncertainties.

Using the simulations described in Section~\ref{sec:sims}

@@

The disruption of a satellite galaxy due to tidal shocking [...connect to Choi work some how?] We model the present-day position and velocity of a disrupted star as the result of sampling from isotropic, log-normal distributions in relative distance, $R=\left\vert \bs{r}-\bs{r}_p \right\vert$, and relative velocity, $V=\left\vert \bs{v}-\bs{v}_p \right\vert$, at the time the star comes unbound from the progenitor, evolved to present day in the parent potential, $\Phi$. The distributions over $\ln R$ and $\ln V$ are centered on the logarithm of the instantaneous tidal radius, $\rtide$, and velocity dispersion, $\sigma_v$, of the progenitor at time $\tau$: $\mathcal{N}(\ln R \given \ln\rtide)\vert_{t=\tau}$ and $\mathcal{N}(\ln V \given \ln \sigma_v)\vert_{t=\tau}$. In this model, we neglect the effect of self-interaction with the halo of the progenitor.

>>>>

\subsection{Scalings}

@@

- Point out constant $\sigma$ over mass\\
- Good until 2.5e9\\
- Proper description models 2D distribution, but [...]

%a phase-space distance, $D_{ps}$, as the sum of the normalized, relative position, $\frac{\bs{r}-\bs{r}_p}{\rtide}$, and velocity, $\frac{\bs{v}-\bs{v}_p}{v_{\rm esc}}$, for a stream star. We minimized the generalized variance of the 6D distribution over each normalized coordinate evaluated at the time that each star has minimum $D_ps$. This simple idea proved quite powerful for constraining properties of the LM10 potential used simulated observations of their N-body simulation. However, this method does not properly incorporate observational uncertainties.

@@

We model the present-day position and velocity of a disrupted star as the result of sampling from isotropic, log-normal distributions in relative distance, $R=\left\vert \bs{r}-\bs{r}_p \right\vert$, and relative velocity, $V=\left\vert \bs{v}-\bs{v}_p \right\vert$, at the time the star comes unbound from the progenitor, evolved to present day in the parent potential, $\Phi$. The distributions over $\ln R$ and $\ln V$ are centered on the logarithm of the instantaneous tidal radius, $\rtide$, and velocity dispersion, $\sigma_v$, of the progenitor at time $\tau$: $\mathcal{N}(\ln R \given \ln\rtide)\vert_{t=\tau}$ and $\mathcal{N}(\ln V \given \ln \sigma_v)\vert_{t=\tau}$. In this model, we neglect the effect of self-interaction with the halo of the progenitor.
